Making all equalities equal

### 2021-09-21 paper.lagda.tex
used sym-Equality

  module _ (_≣_ : ≣-Type) where
    sym-Equality : (≡-≡-≣ : {x y : A} → let
      x≡y : Type (ℓ-max a ℓ)
      x≡y = x ≡ y
      x≣y = x ≣ y
      in x≡y ≡ x≣y)
      → IsEquality _≣_
    sym-Equality ≡-≡-≣ = eq (sym ≡-≡-≣)

@@

\begin{code}
  instance
    ≡p-IsEquality : IsEquality {A = A} _≡p_
    ≡p-IsEquality = eq (λ {x y} → sym λ i → p-c {x = x} {y = y} i)
\end{code}

@@

\begin{code}
  instance
    ≃-IsEquality : IsEquality
      {A = Type ℓ} _≃_
    ≃-IsEquality = eq λ {A B} → sym
      λ i → univalencePath' {A = A} {B = B} i
\end{code}

@@

      instance
        ≡₂-Equality₃ : IsEquality₃ _≡₂_
        ≡₂-Equality₃ = eq α
          where
            open IsEquality eq₃
            α : ∀ {x y} → (x ≡₂ y) ≡₃ (x ≡₁ y)
            α {x} {y} = let
              α₁ = ≣-≡-≡ {x ≡₂ y} {x ≡₁ y}
              α₂ = IsEquality₂.≣-≡-≡ ≡₂-Equality₂ {x} {y}
              in transport (sym α₁) α₂

>>>>

  module _ {_≣_ : ≣-Type} where
    sym-Equality : (≡-≡-≣ : {x y : A} → let
      x≡y : Type (ℓ-max a ℓ)
      x≡y = x ≡ y
      x≣y = x ≣ y
      in x≡y ≡ x≣y)
      → IsEquality _≣_
    sym-Equality ≡-≡-≣ = eq (sym ≡-≡-≣)

@@

\begin{code}
  instance
    ≡p-IsEquality : IsEquality {A = A} _≡p_
    ≡p-IsEquality = sym-Equality (λ {x y} → λ i → p-c {x = x} {y = y} i)
\end{code}

@@

\begin{code}
  instance
    ≃-IsEquality : IsEquality
      {A = Type ℓ} _≃_
    ≃-IsEquality = sym-Equality λ {A B} →
      λ i → univalencePath' {A = A} {B = B} i
\end{code}

@@

      instance
        ≡₂-Equality₃ : IsEquality₃ _≡₂_
        ≡₂-Equality₃ = eq α
          where
            open IsEquality eq₃
            α : ∀ {x y} → (x ≡₂ y) ≡₃ (x ≡₁ y)
            α = transport ≡-≡-≣ (IsEquality₂.≣-≡-≡ ≡₂-Equality₂)
